### 2013-11-12 paper/intro.tex
major changes to formulation part
Add more citations

@@

In this work, we aim to perform an uncertainty quantification
using Polynomial Chaos Expansion. Quantity of interest is the surface elevation.
The uncertainty in the manning coefficient is investigated.
We assume that the Manning coefficient vary by region. Specifically,
we set three values for the manning coefficient namely, at the land (denoted by N1)
and at the shore (denoted by N2) and below the water (denoted by N3).
Uniform distribution is assumed as the prior for the three manning coefficients.
such that UN = [0.005-0.2]. The three regions are shown in Figure~\ref{fig:setup}(right)

>>>>

%!TEX root = paper.tex

@@

In this work, we aim to perform an uncertainty quantification
using Polynomial Chaos Expansion. Quantity of interest is the surface elevation.
The uncertainty in the manning coefficient is investigated.
We assume that the Manning coefficient vary by region. Specifically,
we set three values for the manning coefficient namely, at the land (denoted by N1)
and at the shore (denoted by N2) and below the water (denoted by N3).

\cite{sraj:2013a}
\cite{sraj:2013b}

Background literature on friction coefficient sensitivity:
\begin{itemize}
    \item \cite{Myers:2001el} - Crude friction coefficient sensitivity, found it to be important but not fully explored
    \item \cite{Jakeman:2010hk} - Again a crude (two coefficient) sensitivity analysis.
    \item \cite{Dao:2007hr} - Really not a very good paper, also crude SA.
\end{itemize}

### 2013-11-12 paper/tsunami.tex
Add more citations

Background literature so far
\begin{itemize}
    \item Myers and Baptista (2001) - Crude friction coefficient sensitivity, found it to be important but not fully explored
    \item Jakeman et al (2010) - Again a crude (two coefficient) sensitivity analysis.
    \item Dao and Tkalich (2007) - Really not a very good paper, also crude SA.
\end{itemize}

\section{Numerical Model}

\section{T\={o}hoku Tsunami}
Our study focuses on quantifying ocean wave uncertainties associated with 
manning friction coefficient,

The setting chosen for our experiment is the tsunami in the Pacific ocean 
that occurred in 11 March 2011. The 2011 earthquake off the Pacific coast of Tōhoku lasting approximately six minutes

%The earthquake, caused by 6 to 8 meters upthrust on a 180-km wide seabed at 60 km offshore from the east coast of Tōhoku, resulted in a major tsunami that brought destruction along the Pacific coastline of Japan's northern islands. Thousands of lives were lost when entire towns were devastated. The tsunami propagated throughout the Pacific Ocean region reaching the entire Pacific coast of North and South America from Alaska to Chile

\subsection{GeoClaw}
2D Shallow water equations

>>>>

\section{Approach}

% Our study focuses on quantifying the surface displacement uncertainties associated with the Manning's-N friction coefficient.  The analysis was applied to the \tohoku tsunami

% \tohoku

% \subsection{\tohoku Tsunami}

\subsection{Numerical Model}

Based on work by \cite{MacInnes:2013cr}, \cite{Berger:2011du}, \cite{Berger:2011vi}

\subsection{Observations}
